Borders and Gateways: Measuring and Analyzing National AS Chokepoints

### 2018-07-31 Paper/chokepoint.tex
writing pass

We define a BGP path of length $n$ from source AS $a_0$ to destination AS $a_n$
as a sequence $p_{1\rightsquigarrow n} = \{a_i : i \in [1,n]\}$.  We define a
\textit{routing tree} to be a tree rooted at a single destination AS and
composed of every acceptable BGP path from the various source ASes that can
reach the destination AS.\Ben[inline]{Is this always a tree? Seems like it
could be a DAG sometimes (especially if random choices are made). Also do we
need to define routing trees if we only really work on the path}  The
chokepoint potential of a border AS is the ratio of paths intercepted by that
border AS to the number of paths intercepted by all border ASes belonging to
the same nation. Formally, for a country $c$, let $P = \{p_{i \rightsquigarrow
j} : g(a_i)=c \text{ and } g(a_j)\neq c\} $, i.e.\ the set of all path
originating in $c$ and ending in outside $c$. Then the chokepoint potential,
$cp(\cdot)$, of a border AS $a_u$ with $g(a_u) = c$ is

\begin{equation}
  \label{eq:chokepoint}
  cp(a_u) = \frac{|\{p: p \in P \text{ and } a_u \in P\}|}{|P|}
\end{equation}

The above definition is specifically for capturing paths originating in country
$c$ and routing outside the country, which we will refer to as
\textit{outgoing} chokepoint potential or $cpo$. We can similarily define
\textit{incoming} chokepoint potential or $cpi$, by simply redefining $P$ as $\{p_{i
\rightsquigarrow j}: g(a_i) \neq c \text{ and } g(a_j) = c\}$. That is all
paths originating outside of $c$ but terminating in $c$ and recomputing
Equation~\ref{eq:chokepoint}.

@@

Given a set of routing trees\Ben[inline]{paths?}, chokepoint potential is an intuitive way to
compare individual ASes. With this measure, the sum of the chokepoint potential
for all border ASes for a country is 1.0, as in, all of the border ASes
collectively control the flow of information over the nation's border. We
define the aggregate \emph{national chokepoint potential} as the number of
border ASes required to control a particular fraction $f$ of paths. Formally,
given a country,$c$, with a set of $k$ border ASes $\{a_1,a_2,\cdots,a_k\}$ with
$cp(a_i)>cp(a_j) \forall i<j$ (i.e.\ sorted in descending order), the
we find the smallest $j$ such that

@@

and define national chokepoint potential as $CP(c,f) = 1/j$. We use the
multiplicative inverse here to preserve a clearer semantic meaning i.e.\ higher
chokepoint potential implies more control over paths. The more border ASes
required, the more difficult it would likely be for that nation to perform
censorship or surveillance, as the government would have to restrict more ISPs,
place more filtering hardware, etc. 
%Thus, we can define another measure, with
%this one being a national measure. We define the \emph{national breakthrough
%potential} of a nation to be the minimum number of ASes required to intercept a
%selected percentage of AS-level paths. 
Previous work has used $f=0.90$ as a benchmark indicating strong control of information
\cite{throats}, so we use this percentage as well. When used here, however,
90\% path interception indicates a single nation intercepts 90\% of the paths
that either enter said nation (for the out-to-in case) or exit said nation (for
the in-to-out case). National breakthrough potential is calculated taking the
strongest ASes first, such that the measure reflects the smallest number of
border ASes needed to intercept the paths.\footnote{We note that a dual measure
could be defined as the fraction of paths controlled by $j$ ASes. Our results
are substantively the same for either definition.\Ben[inline]{Check to make
sure}}.

We measure the absolute number of ASes required to control a specific
fraction rather than a percentage within a country because it makes for more
equitable comparisons between nations
Take for instance the United States, which has many more ASes than
most nations. If the United States and another nation both required the same
percentage of border ASes to intercept 90\% of paths, the similarity of these
nations would be misleading. Controlling the larger absolute number of ASes
would require significantly more resources.\Ben[inline]{we need to actually
pick another nation where this is true to make this example illustrative.} Our technique provides a comparison more likely to
reflect reality. 
%This measure is called a breakthrough potential because it
%indicates the number of border ASes that intercept a vast majority of paths,
%meaning that a country with high NBP would require controlling many border ASes
%to prevent a breakthrough, or an unfettered access of internal ASes to that
%country.

>>>>

We define a BGP path of length $n$ from source AS $a_0$ to destination AS $a_n$
as a sequence $p_{1\rightsquigarrow n} = \{a_i : i \in [1,n]\}$.  We define a
\textit{routing tree} to be a tree rooted at a single destination AS and
composed of every acceptable BGP path from the various source ASes that can
reach the destination AS.\Ben[inline]{Is this always a tree? Seems like it
could be a DAG sometimes (especially if random choices are made). Also do we
need to define routing trees if we only really work on the path}  The
chokepoint potential of a border AS is the ratio of the number of paths in (or out of) the country that contain the border AS to
the total number of paths in (or out of) the same country.
%intercepted by all border ASes belonging to
%the same nation.
Formally, for country $c$, let $P = \{p_{i \rightsquigarrow
j} : g(a_i)=c \text{ and } g(a_j)\neq c\} $, i.e.\ the set of all paths
originating in $c$ and ending outside $c$. Then the chokepoint potential,
$cp(\cdot)$, of a border AS $a_u$ with $g(a_u) = c$ is
\Steph[inline]{How do we count a parth that originates in a country, routes through a different country, and terminates in the original country?  That case is relevant in US law.}
\begin{equation}
  \label{eq:chokepoint}
  cp(a_u) = \frac{|\{p: p \in P \text{ and } a_u \in P\}|}{|P|}
\end{equation}

The above definition applies to paths originating in country
$c$ and routing to a different country, which we will refer to as
\textit{outgoing} chokepoint potential or $cpo$. We similarily define
\textit{incoming} chokepoint potential or $cpi$, by redefining $P$ as $\{p_{i
\rightsquigarrow j}: g(a_i) \neq c \text{ and } g(a_j) = c\}$. That is all
paths originating outside of $c$ but terminating in $c$ and recomputing
Equation~\ref{eq:chokepoint}.

@@

% SF says 'paths' in response to Ben
Given a set of BGP paths, chokepoint potential is an intuitive way to
compare individual ASes. Note that the sum of the chokepoint potentials
for all border ASes for a given country is 1.0.
%, as in, all of the border ASes
%collectively control the flow of information over the nation's border.
We define the aggregate \emph{national chokepoint potential} as the number of
border ASes required to control a particular fraction $f$ of paths. Formally,
given a country,$c$, with a set of $k$ border ASes $\{a_1,a_2,\cdots,a_k\}$ with
$cp(a_i)>cp(a_j) \forall i<j$ (i.e.\ sorted in descending order), we find the smallest $j$ such that

@@

and define national chokepoint potential as $CP(c,f) = 1/j$. The
multiplicative inverse preserves a clearer semantic meaning i.e.\ higher
chokepoint potential implies more control over paths. The fewer border ASes
required to control $f$ paths, the easier it is to perform
censorship or surveillance, e.g., by restricting ISPs,
placing filtering hardware, etc. 
%Thus, we can define another measure, with
%this one being a national measure. We define the \emph{national breakthrough
%potential} of a nation to be the minimum number of ASes required to intercept a
%selected percentage of AS-level paths. 
Previous work used $f=0.90$ as a threshold indicating strong control of information
\cite{throats}, so we use this percentage as well. When used here, however,
90\% path control indicates the percentage of paths into (our out of) a country.
%that a single nation intercepts 90\% of the paths
%that either enter said nation (for the out-to-in case) or exit said nation (for
%the in-to-out case).
National chokepoint potential is calculated
%by taking the
%strongest ASes first, such that the measure
as the smallest number of
border ASes needed to control $f$ of the paths.\footnote{We note that a dual measure
could be defined as the fraction of paths controlled by $j$ ASes. Our results
are substantively the same for either definition.\Ben[inline]{Check to make
sure}}.

We measure the absolute number of ASes required to control a specific
fraction rather than a percentage within a country to make
comparisons between nations more equitable.
Consider, for instance, the United States, which has many more ASes than
most nations. If the United States and another nation both required the same
percentage of border ASes to intercept 90\% of paths, the similarity of these
nations would be misleading because the cost of controlling the larger absolute number of ASes
would be significantly higher.\Ben[inline]{we need to actually
pick another nation where this is true to make this example illustrative.} Our technique provides a comparison more likely to
reflect reality. 
%This measure is called a breakthrough potential because it
%indicates the number of border ASes that intercept a vast majority of paths,
%meaning that a country with high NBP would require controlling many border ASes
%to prevent a breakthrough, or an unfettered access of internal ASes to that
%country.
